---
output:
  pdf_document:
    latex_engine: xelatex
    fig_caption: yes
    keep_tex: yes
fontsize: 8pt
geometry: "left=1cm,right=1cm,top=2cm,bottom=2cm"
header-includes: 
  \usepackage{fancyhdr} 
  \pagestyle{fancy}
  \usepackage{graphicx} 
  \usepackage{eurosym} 
  \usepackage{xcolor}
  \usepackage{booktabs,xcolor}
  \definecolor{myblue}{HTML}{5F7ED9}
  \rhead{\includegraphics[width=4cm]{gender-logo.png}}
  \lhead{\includegraphics[width=1.25cm]{Flag_of_Colombia.png}\fontsize{20}{1}\selectfont\textbf{ COLOMBIA \textcolor{myblue}{GENDER LANDSCAPE}}}
  \rfoot{}  
  \lfoot{\includegraphics[width=19.5cm]{footerpdf.pdf}} 
  \fancypagestyle{plain}{\pagestyle{fancy}} 
  \pagenumbering{gobble}
  \usepackage{pagecolor}
  \usepackage[defaultfam,tabular,lining]{montserrat}
  \usepackage[fontsize=8pt]{scrextend}
  \usepackage{float}
  \restylefloat{table}
  \usepackage{multicol}
  \newcommand{\hideFromPandoc}[1]{#1}
  \hideFromPandoc{
    \let\Begin\begin
    \let\End\end
  }
  \usepackage{caption}
  \captionsetup{skip=0pt} 
---
\textcolor{white}{.}
  \vspace{6pt}
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
options(knitr.table.format = "latex")

library(wbstats)
library(tidyverse)
library(kableExtra)
library(knitr)
library(ggplot2)
library(maps)
library(viridis)
library(cowplot)


load("mapregion.RData")
load("wbtable.RData")
load("callouts.RData")
load("resources.RData")
load("lawchart.RData")
load("regionallinks.RData")
load("globallinks.RData")
load("introtext.RData")
country_run <- "Colombia"

```

```{r legend, include=T, echo = F,warning=F,out.width= "25%"}
dt <- mtcars[1:5, 1:6]
kbl(dt) %>%
  kable_styling(bootstrap_options = "striped", full_width = F, position = "float_right")
```

The brief provides a quick overview of the gender landscape in Colombia on some key indicators. Promoting gender equality is critical to reducing poverty, boosting shared prosperity, achieving a just transition and sustainable growth. For `r country_run`, the highest performing indicators relative to the baseline year are `r introtext[[1]][1]` and `r introtext[[1]][2]`. The largest declines relative to the baseline year are `r introtext[[1]][15]` and `r introtext[[1]][14]`.

\renewcommand{\arraystretch}{1.1}

```{r table, include=T, echo = F,warning=F}

footnote <- "Data retrieved from World Bank Gender Data Portal. Country Baseline provides a reference point for the indicator, circa 2000. Modeled ILO estimate LAC = Includes the 42 countries (all income levels) in Latin America and the Caribbean, as classified by The World Bank Group. UMC = In FY21, upper- middle-income countries are those with a GNI per capita between $4,046 and $12,535 (calculated using the World Bank Atlas method)"

wb_table %>% 
  head(.,nrow(.)-8) %>% 
  select(-c(1,2,12:16)) %>% 
  kbl(booktabs = T,longtable = T) %>% 
  column_spec(1,width = "9cm",link = wb_table$vlinks) %>% 
  column_spec(2:9,width = ".85cm") %>% 
  column_spec(5,color = "black",bold = T,
              background = spec_color(wb_table$RegionChange, end = 0.8,begin = 0.4, na_color = "lightgray",option = "turbo")) %>%
  column_spec(6,image = spec_image(wb_table$iconRegion, 30, 30)) %>%
  pack_rows("HUMAN ENDOWMENTS",1,11,background = "lightgray",indent = F,hline_after = T) %>% 
  pack_rows("ECONOMIC OPPORTUNITY",12,25,background = "lightgray",indent = F,hline_after = T) %>% 
  pack_rows("VOICE AND AGENCY",26,32,background = "lightgray",indent = F,hline_after = T) %>% 
  kable_styling(latex_options=c("hold_position", 
                                "repeat_header"),
                font_size = 7.5) %>%
  add_header_above(c(" " = 2, "Columbia's Performance" = 4, "Peers Comparison" = 3
                     )) %>% 
  collapse_rows(.,columns = 1,valign = "middle",latex_hline = "major") %>% 
  footnote(footnote_as_chunk = TRUE,
           threeparttable = TRUE,
           general = footnote)
```
\newpage
  .  
  
\fontsize{14}{8}\selectfont
Gender Equality in Colombia
\normalsize

```{r calls, include=T, echo = F,warning=F}
callouts %>% 
  kbl(booktabs = T,longtable = F) %>% 
  kable_styling(full_width = T) %>% 
  row_spec(row = 0,font_size = 22,bold = T,color = "#9966CC") %>% 
  row_spec(row = 1,font_size = 8,bold = F,color = "black",italic = T,background = "lightgray") 
#wb_table %>% 
#  select(-c(1,2,4,5,7:11)) %>% 
#  slice_tail(.,n = 8) %>% 
#  kbl(booktabs = T,longtable = F) %>% 
#  kable_styling(font_size = 10,full_width = F,position = "float_left") %>% 
#  column_spec(1,width = "3.5cm") %>% 
#  column_spec(2,width = "1.5cm") %>% 
#  column_spec(1:2,color = "white",
#             background = spec_color(wb_table$Rating[31:38], end = 0.6))

```

\fontsize{14}{8}\selectfont
Gender Equality and the Law
\normalsize

Women, Business and the Law 2021 presents an index covering 190 economies and structured around the life cycle of a working woman. In total, 35 questions are scored across the eight indicators. Colombia scores 81.9 out of 100, higher than the regional average observed across Latin America & Caribbean (80.1).
```{r genderlaw, include=T, echo = F,warning=F,out.width="100%",fig.align='center',out.extra='trim={0 3.1cm 0 3.1cm},clip'}
plot_grid(map_region,NULL,lawchart,rel_widths = c(12,3,17),align = "h",nrow = 1,ncol = 3)
```

***

\fontsize{14}{8}\selectfont
Curated resources to address gender gaps
\normalsize

Click on the links below for more information

```{r links, include=T, echo = F,warning=F,out.extra='trim={0 3.1cm 0 3.1cm},clip'}

resources %>% 
  kbl(booktabs = T, longtable = F) %>% 
  kable_styling(font_size = 8,full_width = F,
                position = "float_left") %>% 
  column_spec(1,link = globallinks,width = '9cm') %>% 
  column_spec(2,link = regionallinks,width = '9cm') %>%
  row_spec(row = 0,font_size = 10,bold = T) %>% 
  pack_rows("Human Endowments",1,3,latex_align = "c")%>% 
  pack_rows("Economic Opportunity",4,7,latex_align = "c") %>% 
  pack_rows("Voice and Agency",8,9,latex_align = "c") %>% 
  pack_rows("Girls Green, Resilient, & Economic Development",10,11,latex_align = "c") 

```
