---
output: 
  pdf_document:
    latex_engine: xelatex
    fig_caption: yes
    keep_tex: yes
geometry: "left=1cm,right=1cm,top=2cm,bottom=2cm"
header-includes: 
  \usepackage{fancyhdr} 
  \pagestyle{fancy}
  \usepackage{graphicx} 
  \usepackage{eurosym} 
  \usepackage{xcolor}
  \usepackage{booktabs,xcolor}
  \definecolor{myblue}{HTML}{5F7ED9}
  \definecolor{wblight}{HTML}{f8f4fc}
  \rhead{\includegraphics[width=3.5cm]{gender-logo.png}}
  \lhead{\includegraphics[width=1.25cm]{Flag_of_Colombia.png}\fontsize{22}{1}\selectfont\textbf{ COLOMBIA \textcolor{myblue}{GENDER LANDSCAPE}}}
  \rfoot{Last compiled on `r format(Sys.time(), '%d %B, %Y')`}  
  \lfoot{\includegraphics[width=19.5cm]{footer.png}} 
  \fancypagestyle{plain}{\pagestyle{fancy}} 
  \pagenumbering{gobble}
  \usepackage[defaultfam,tabular,lining]{montserrat}
  \usepackage[fontsize=8pt]{scrextend}
  \usepackage{float}
  \restylefloat{table}
  \usepackage{multicol}
  \newcommand{\hideFromPandoc}[1]{#1}
  \hideFromPandoc{
    \let\Begin\begin
    \let\End\end
  }
  \usepackage{caption}
  \captionsetup{skip=0pt} 
  \setlength{\headsep}{1.1cm}
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
options(knitr.table.format = "latex")

library(wbstats)
library(tidyverse)
library(kableExtra)
library(knitr)
library(ggplot2)
library(maps)
library(viridis)
library(cowplot)


load("mapregion.RData")
load("wbtable.RData")
load("callouts.RData")
load("resources.RData")
load("lawchart.RData")
load("regionallinks.RData")
load("globallinks.RData")
load("introtext.RData")
country_run <- "Colombia"

```

```{r legend, include=T, echo = F,warning=F}
Comparison <- c("Higher Performance", "Equal/No Change", "Lower Performance", "No Data")
Baseline <- c("","","","")
Region <- c(" "," "," "," ")
data.frame(Comparison,Baseline,Region) %>% 
kbl(booktabs = T,toprule = "",bottomrule = "") %>%
  kable_styling(full_width = F, position = "float_right",font_size = 8,bootstrap_options = "none") %>% 
    column_spec(3,background = spec_color(c(1,2,3,NA), end = 0.8,begin = 0.4, na_color = "lightgray",option = "turbo")) %>%
  column_spec(2,image = spec_image(c("upicon.png","righticon.png","downicon.png","naicon.png"), 30, 30)) %>% 
  row_spec(0,bold = T)

```
\fontsize{9}{8}\selectfont
This brief provides a quick overview of the gender landscape in Colombia on some key indicators. For `r country_run`, the highest performing indicators relative to the baseline year are `r introtext[[1]][1]` and `r introtext[[1]][2]`. The largest declines relative to the baseline year are `r introtext[[1]][15]` and `r introtext[[1]][14]`.
\normalsize
\vspace{2pt}
  
\renewcommand{\arraystretch}{1.15}

```{r table, include=T, echo = F,warning=F}

footnote <- "Data retrieved from World Bank Gender Data Portal. Country Baseline provides a reference point for the indicator, circa 2010. LAC = Includes the 42 countries (all income levels) in Latin America and the Caribbean, as classified by The World Bank Group. UMC = In FY21, upper- middle-income countries are those with a GNI per capita between $4,046 and $12,535 (calculated using the World Bank Atlas method)."

wb_table %>% 
  head(.,nrow(.)-9) %>% 
  select(-c(1,11:18)) %>% 
  kbl(booktabs = T,longtable = T) %>% 
  column_spec(1,width = "9cm",link = wb_table$vlinks) %>% 
  column_spec(2:9,width = ".85cm") %>% 
  column_spec(5,color = "black",bold = T,
              background = spec_color(wb_table$RegionChange, end = 0.8,begin = 0.4, na_color = "lightgray",option = "turbo")) %>%
  column_spec(6,image = spec_image(wb_table$iconRegion, 30, 30)) %>%
  pack_rows("HUMAN ENDOWMENTS",1,11,background = "lightgray",indent = F,hline_after = T) %>% 
  pack_rows("ECONOMIC OPPORTUNITY",12,25,background = "lightgray",indent = F,hline_after = T) %>% 
  pack_rows("VOICE AND AGENCY",26,32,background = "lightgray",indent = F,hline_after = T) %>% 
  kable_styling(latex_options=c("hold_position", 
                                "repeat_header"),
                font_size = 8,full_width = F) %>%
  add_header_above(c(" " = 2, "Columbia's Performance" = 4, "Peers Comparison" = 3
                     )) %>% 
  collapse_rows(.,columns = 1,valign = "middle",latex_hline = "major") %>% 
  footnote(footnote_as_chunk = TRUE,
           threeparttable = TRUE,
           general = footnote)
```

\newpage
\clearpage 

\fontsize{14}{8}\selectfont
Gender Equality in Colombia
\normalsize

\fboxrule.6pt\fboxsep6pt
\fcolorbox{myblue}{wblight}{\color{black}
\begin{minipage}[c][2.5cm][t]{3.45cm}
\raggedright\fontsize{12}{1}\selectfont   
\textbf{`r callouts[[5]][1]`} 
\normalsize
  
\vspace{.3cm}
  
\emph{`r callouts[[4]][1]`}
\end{minipage}} 
\fcolorbox{myblue}{wblight}{\color{black}
\begin{minipage}[c][2.5cm][t]{3.45cm}
\raggedright\fontsize{12}{1}\selectfont   
\textbf{`r callouts[[5]][2]`} 
\normalsize
  
\vspace{.3cm}
 
\emph{`r callouts[[4]][2]`}
\end{minipage}} 
\fcolorbox{myblue}{wblight}{\color{black}
\begin{minipage}[c][2.5cm][t]{3.45cm}
\raggedright\fontsize{12}{1}\selectfont   
\textbf{`r callouts[[5]][3]`} 
\normalsize
  
\vspace{.3cm}
 
\emph{`r callouts[[4]][3]`}
\end{minipage}} 
\fcolorbox{myblue}{wblight}{\color{black}
\begin{minipage}[c][2.5cm][t]{3.45cm}
\raggedright\fontsize{12}{1}\selectfont   
\textbf{`r callouts[[5]][4]`} 
\normalsize
  
\vspace{.3cm}
 
\emph{`r callouts[[4]][4]`}
\end{minipage}} 
\fcolorbox{myblue}{wblight}{\color{black}
\begin{minipage}[c][2.5cm][t]{3.45cm}
\raggedright\fontsize{12}{1}\selectfont   
\textbf{`r callouts[[5]][5]`} 
\normalsize
  
\vspace{.3cm}
 
\emph{`r callouts[[4]][5]`}
\end{minipage}}
\vspace{.2cm}
    
\fontsize{14}{8}\selectfont
Gender Equality and the Law
\normalsize

Women, Business and the Law 2021 presents an index covering 190 economies and structured around the life cycle of a working woman. In total, 35 questions are scored across the eight indicators. Colombia scores 81.9 out of 100, higher than the regional average observed across Latin America & Caribbean (80.1).
```{r genderlaw, include=T, echo = F,warning=F,out.width="100%",fig.align='center',out.extra='trim={0 3.1cm 0 3.1cm},clip'}
plot_grid(map_region,NULL,lawchart,rel_widths = c(12,3,17),align = "h",nrow = 1,ncol = 3)
```

***

\fontsize{14}{8}\selectfont
Curated resources to address gender gaps
\normalsize

Click on the links below for more information

```{r links, include=T, echo = F,warning=F,out.extra='trim={0 3.1cm 0 3.1cm},clip'}

resources %>% 
  kbl(booktabs = T, longtable = F) %>% 
  kable_styling(font_size = 8,full_width = F,
                position = "float_left") %>% 
  column_spec(1,link = globallinks,width = '9cm') %>% 
  column_spec(2,link = regionallinks,width = '9cm') %>%
  row_spec(row = 0,font_size = 10,bold = T) %>% 
  pack_rows("Human Endowments",1,3,indent = F,latex_align = "c")%>% 
  pack_rows("Economic Opportunity",4,7,indent = F,latex_align = "c") %>% 
  pack_rows("Voice and Agency",8,9,indent = F,latex_align = "c") %>% 
  pack_rows("Girls Green, Resilient, & Economic Development",10,11,indent = F,latex_align = "c") 

```
